How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-06-11 templates/paper.tex
wrote a couple of paragraphs of introduction

reveal the hidden curriculum -- what's expected of a software consumer, how to
ask for help, how to contribute

@@

\begin{checklist}{A good community}
\begin{itemize}
\item Helps users solve their problems
\item Is friendly and supportive when responding to questions
\item Encourages participation from users of all experience levels
\item Encourages respectful treatment of all community members, and calls out disrespectful behavior
\end{itemize}
\end{checklist}

>>>>

Most practicing scientists (even the ones who write code as part of their
research) spend more time as consumers as opposed to producers of software.
Moreover, we are constantly learning new skills and solving new problems, which
often means learning to use new programs or new aspects of large packages. This,
combined with the complex nature of scientific software (and the often low
quality of the associated documentation) means we have to ask for help.
Sometimes it's because we don't know how to accomplish a specific task. Others,
it's because there's a feature we need that isn't implemented. Inevitably, there
are bugs.

In all of these cases, it is necessary to interact with the folks who develop
and support the code. How you go about it has an enormous impact on your
likelihood of success and how you are viewed, but this is not something that is
explicitly taught in most places.  {\emph The goal of this work is to reveal the hidden
curriculum -- what's expected of a software consumer, how to ask for help, how
to contribute productively to a software community (regardless of whether you
can write code).}

There lots of articles on best practices in software development, including open
source.

@@

\begin{checklist}{A good community}
\begin{itemize}
\item Helps users solve their problems
\item Is friendly and supportive when responding to questions
\item Is receptive to suggestions and critiques, regardless of the source
\item Encourages participation from users of all experience levels
\item Encourages respectful treatment of all community members, and calls out disrespectful behavior
\end{itemize}
\end{checklist}
